RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-12 doc/paper.tex
Intro: working...

	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP). Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming. A differential evolution algorithm was proposed by Cerny et al.~\cite{cerny2008using}. Application of local--based heuristics on solving SR is discovered in~\cite{kommenda2018local}.

>>>>

	 There are many different ways to tackle the SR by achieving the right analytic expressions, some of them are more related to machine learning techniques, others exploiting the technique of genetic programming (GP) and various approximate methods such as meta-heuristics. Among the first GP methods to tackle SR is the one of Raidl~\cite{raidl1998hybrid} based on a hybrid variant of genetic programming. A differential evolution algorithm was proposed by Cerny et al.~\cite{cerny2008using}. Age-fitness Pareto Optimization approach is proposed by Smidt and Lipson~\cite{schmidt2010age}.  
	 Application of local--based heuristics on solving SR is discusses by Commenda in his Ph.D. thesis~\cite{kommenda2018local}. A  GP-based approach, the gene-pool optimal mixing evolutionary algorithm (GOMEA) is studied by Virgolin et al.~\cite{virgolin2021improving}.  Another evolutionary algorithm, the interaction-transformation EA (ITEA) has been proposed by de Franca et al.~\cite{de2021interaction}. Simulated annealing to solve SR is proposed by Kantor~\cite{kantor2021simulated}.
